Untwisting the Tetrahelix (v0.6)

### 2017-02-25 doc/TetrahelixUntwist.tex
proofs strengthened but still crummy

\section{Optimal Tetrahelices Have Evenly Spaced Vertices}

We use the term \emph{tetrahelix} to mean any structure made of
vertices and edges which is isomorphic to the BC helix, in which the
vertices lie on three helices, no matter what lengths the edges take
on. One could consider various definitions of optimality for a
tetrahelix, but the must useful to an enginner is to minimize the
maximum difference between any two edges. We call a tetrahelix
\emph{member-length minimax optimal} (or just \emph{optimal}) if there is not tetrahelix of the
same radius and pitch with a smaller maximum edge length difference.

Consider a tetrahelix isomporphic to an BC helix of unbounded
extent. If all three rails do not have same pitch, there is an edge of
unbounded length. So we are justified in talking about the pitch of
the tetrahelix, even though we think of it as three
helices. Similarly, if the axes are not parallel, there is an edge of
unbounded length in the structure, so it is not optimal.

Consider any tetrahelix in which the axes of the helices are parallel
to $z$ but not coincident, but in which all three helices have the
same radius. Consider the projection along the $z$ axis, which will be
a figure of dots and connecting segments in the $xy$ plane. The convex
hull for any one helix projection will be a circle (if its pitch is
irrational) or an polygon if rational. So long as its rail angle is
not $0$, it will have at least two points in the plane. One of these
will be longer and will be made shorter by moving that helix closer to
the midpoint of the other two in the $xy$ plane. Even if the rail
angle is $\pi$, there will be two vertices for each rail, each of
which is connected to both vertices of the other two rails. At lesast
one of these lines is a longest line which will be made shorter by
moving that helix in the $xy$ plane closer to the midpoint of the
other two.

>>>>

\section{Optimal Tetrahelices Have $z$-axis Evenly Spaced Vertices}

We use the term \emph{tetrahelix} to mean any structure made of
vertices and edges which is isomorphic to the BC helix, in which the
vertices lie on three helices, no matter what lengths the edges take
on. One could consider various definitions of optimality for a
tetrahelix, but the must useful to an enginner is to minimize the
maximum difference between any two edges.
Define the \emph{projected incircle radius} of a tetrahelix to be
the radius of the incircle of all point on the tetrahelix projected
down the $z$ axis into the $xy$ plane.
We call a tetrahelix
\emph{member-length minimax optimal} (or just \emph{optimal}) if there is not tetrahelix of the
same project incircle radius and pitch with a smaller maximum edge length difference.

Consider a tetrahelix isomporphic to an BC helix of unbounded
extent. If all three rails do not have same pitch, there is an edge of
unbounded length, so it is not optimal. So we are justified in talking about the pitch of
the tetrahelix, even though we think of it as three
helices. Similarly, if the axes are not parallel, there is an edge of
unbounded length in the structure, so it is not optimal. So all three
rails have the same rail length.

We wish to show that the three helices optimal tetrahelix also have
coincident axes.
Consider any tetrahelix in which the axes of the helices are parallel
to $z$ but not coincident, but in which all vertices lie on or outside
a cylinder of radius $r$ centered on the $z$ axis.
Since all three rails have the same rail length, no matter how we
move the rails in the $xy$ plane if we shorten the $xy$ distance between
vertices we shorten the total distance.
Consider the projection along the $z$ axis of all vertices into the $xy$ plane, which will be
a figure of dots and connecting segments in the $xy$ plane. The convex
hull for any one helix projection will be a circle (if its pitch is
irrational) or an polygon if rational, or a point if the helix has
zero curvature. Each of these figures by definitions lies outside the
circle of radius $r$ in the $xy$ plane.
It is easiest to consider helices of zero curvature which only have one point
as a special case. 
For one rail consider a point in this projected figure furthest from the midpoint of the
the two rails. The lengths to the furthest point on the other two rails will
be decreased by moving the axis of that rail closer to the midpoint of the
other two. Such motion 
One of these segements
will be longer and will be made shorter by moving that helix closer to
the midpoint of the other two in the $xy$ plane. Even if the rail
angle is $\pi$, there will be two vertices for each rail, each of
which is connected to both vertices of the other two rails. At lesast
one of these lines is a longest line which will be made shorter by
moving that helix in the $xy$ plane closer to the midpoint of the
other two.

For the special case of degenerate helix where we do not know the angle
of the points from the axis, we can see that we minimize the maximum lengths
when the projected vertices form an equilateral triangle around the $z$ axis at
length $6r/sqrt{3}$.
This is a equivalent to some let of helices which do have their axes on
the $z$ axis, so without loss of generality we treat these degenerate
helices as if they have their axis at the $z$-axis.
